\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2019-06-05 sections/results.tex
Change: Minor grammatical changes

  \subsection*{Networks generated using different network inference methods show marked difference in edge-density and connectivity}

@@

  The taxonomy composition table obtained using the \ac{ncbi} reference database is used as the input to these algorithms to infer co-occurrence associations between the microbes.
  Figure~\ref{fig:figure5}A shows the networks inferred from this dataset using the different inference algorithms.
  An edge weight threshold of 0.3 was applied to the networks generated from the methods that infer pairwise correlations and no threshold was applied in case of the other networks.
  We can clearly see that the different networks differ vastly in their edge-density and connectivity and even some of the edges in common to these networks have their signs inverted.
  To get a more quantitative idea, we can take a look at the nodes and edges (Figure~\ref{fig:figure5}B) in common between the networks using UpSet plots (only \ac{magma}, \ac{mldm}, \ac{spieceasi}, \ac{sparcc} are used for comparison).
  The results for the node intersections show that the networks have a large number of edges in common ($63$ out of $67$ nodes in the smallest network - \ac{magma}) and no network possesses any unique node.
  The edge intersections in contrast show that only $19$ edges (out of $98$ edges in the smallest network - \ac{magma}) are in common between all the methods and each network has a large number of unique edges.
  These results indicate that there is a substantial rewiring of connections in the inferred networks.

@@

  \begin{figure}[h]
    \centering
    \includegraphics[width=0.85\textwidth]{figure5.pdf}
    \caption{
      \textbf{Networks generated using different network inference methods show marked differences both in terms of edge-density and connectivity}.
      \textbf{(A)} The six different networks generated by the different network inference methods are very dissimilar.
      The green links are positive associations and the orange links are negative associations.
      A threshold of 0.3 was set for the methods that infer pairwise correlations (\ac{sparcc}, Spearman, Pearson) and no threshold was set for the other methods.
      \textbf{(B)} The node overlap upset plot indicates that all the networks have a large number of common nodes involved in connections.
      Whereas, \textbf{(C)} The edge overlap upset plot shows that a very small fraction of these connections are actually shared.
    }
    \label{fig:figure5}
  \end{figure}

>>>>

  \subsection*{Networks generated using different network inference methods show notable difference in edge-density and connectivity}

@@

  The taxonomy composition table obtained using the \ac{ncbi} reference database is used as the input to these algorithms to infer co-occurrence associations between the microbes.
  Figure~\ref{fig:figure5}A shows the networks inferred from this dataset using the different inference algorithms.
  An edge weight threshold of 0.3 was applied to the networks generated from the methods that infer pairwise correlations and no threshold was applied in case of the other networks.
  We can clearly see that the different networks differ vastly in their edge-density and connectivity and even some of the edges in common to these networks have their signs inverted.
  To get a more quantitative idea, we can take a look at the nodes and edges (Figure~\ref{fig:figure5}B) in common between the networks using UpSet plots (only \ac{magma}, \ac{mldm}, \ac{spieceasi}, \ac{sparcc} are used in the comparison).
  The results for the node intersections show that the networks have a large number of edges in common ($63$ out of $67$ nodes in the smallest network - \ac{magma}) and no network possesses any unique node.
  The edge intersections in contrast show that only $19$ edges (out of $98$ edges in the smallest network - \ac{magma}) are in common between all the methods and each network has a large number of unique edges.
  These results indicate that there is a substantial rewiring of connections in the inferred networks.

@@

  \begin{figure}[h]
    \centering
    \includegraphics[width=0.85\textwidth]{figure5.pdf}
    \caption{
      \textbf{Networks generated using different network inference methods show notable differences both in terms of edge-density and connectivity}.
      \textbf{(A)} The six different networks generated by the different network inference methods are very dissimilar.
      The green links are positive associations and the orange links are negative associations.
      A threshold of 0.3 was set for the methods that infer pairwise correlations (\ac{sparcc}, Spearman, Pearson) and no threshold was set for the other methods.
      \textbf{(B)} The node overlap upset plot indicates that all the networks have a large number of common nodes involved in connections.
      Whereas, \textbf{(C)} The edge overlap upset plot shows that a very small fraction of these connections are actually shared.
    }
    \label{fig:figure5}
  \end{figure}
